Neighbor-Based Decentralized Training Strategies for Multi-Agent Reinforcement Learning

### 2024-10-12 paper-2024-sac-marl-neighbouring-strategies.tex
add communication overhead

>>>>

The proposed neighbor-based approaches, particularly NN averaging and experience sharing, achieve performance
 comparable to CTDE while maintaining a decentralized learning structure similar to DTDE. 
% 
However, this entails a communication overhead due to the information agents must exchange with their neighbors. 
%
For NN consensus, the overhead remains constant, as each agent selects the best neighbor and only exchanges 
 information with that agent, meaning the amount of data shared does not increase with the number of neighbors. 
% 
In contrast, for NN averaging and experience sharing, the overhead scales linearly. 
%
Specifically, the growth in overhead for experience sharing is minimal, as the agents' experiences require very 
 little memory. 
%
For NN averaging, however, this increase is more significant, as even a moderately complex neural network 
 has a substantially larger memory footprint.
% 
Nevertheless, for all approaches, the overhead remains within a few megabytes (less than 25MB) when dealing with 
 up to 10 neighboring agents.
%
This makes all approaches feasible, although in scenarios with limited communication resources, experience 
 sharing would be the optimal choice, as it provides performance similar to NN averaging but with 
 much lower overhead.
